Workflow for CLM5 paper

### 2018-10-04 Workflow.tex
update of paper files

\begin{document}
\title{Workflow for CLM5 paper}
\maketitle{}

@@

\section{Elevated CO$_{2}$ transient runs}
\subsection{Make elevated CO$_{2}$ file}
Use this script\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/matlab/modify_co2_drivers.m}}}\\
commit 0d4fb93

@@

\subsection{Make elevated CO$_{2}$ defaults}
Use this script:\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/make_site_transient_ELEV_defaults}}}\\
commit 8e6a3a5

@@

\subsection{Make elevated CO$_{2}$ ensemble}
Use this script:\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/make_site_transient_ELEV_ensembles}}}\\
commit ffe1b6b

>>>>

\begin{document}
\title{Workflow for CLM5 paper}

@@

\subsection{Elevated CO2}
\subsection{Make elevated CO2 file}
Use this script\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/matlab/modify_co2_drivers.m}}}\\
commit 0d4fb93

@@

\subsection{Make elevated CO2 defaults}
Use this script:\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/make_site_transient_ELEV_defaults}}}\\
commit 8e6a3a5

@@

\subsection{Make elevated CO2 ensemble}
Use this script:\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/make_site_transient_ELEV_ensembles}}}\\
commit ffe1b6b

### 2018-10-04 figures.tex
update of paper files

\documentclass[draft,linenumbers]{agujournal}
\draftfalse
\usepackage{hyperref}

@@

\journalname{Journal of Advances in Modeling Earth Systems (JAMES)}
\begin{document}
 \begin{figure}[h]
     \centering
     \includegraphics[width=35pc]{matlab/figures/frac_deviation_p1CLM5_CAX__y1.png}
     \caption{Caxiuana State Parameter Sensitivity}
     \label{CAX state}
  \end{figure}

   \begin{figure}[h]
     \centering
     \includegraphics[width=35pc]{matlab/figures/frac_deviation_p1CLM5_BCI__y1.png}
     \caption{BCI State Parameter Sensitivity}
     \label{BCI state}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=35pc]{matlab/figures/frac_deviation_p1CLM5_ORN__y1.png}
     \caption{Oak Ridge State Parameter Sensitivity}
     \label{ORN state}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=35pc]{matlab/figures/frac_deviation_CO2_response_1CLM5_1x1pt_Br-cax_ens_transient_ELEV_PI_y1.png}
     \caption{Response to Nitrogen Deposition}
     \label{Caxiuana CO2 response Parameter Sensitivity }
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=35pc]{matlab/figures/frac_deviation_CO2_response_1CLM5_1x1pt_US-ORN_ens_transient_ELEV_PI_y1.png}
     \caption{Response to Nitrogen Deposition}
     \label{Oak Ridge CO2 response Parameter Sensitivity}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=35pc]{matlab/figures/frac_deviation_CO2_response_1CLM5_BCI__y1.png}
     \caption{Response to Nitrogen Deposition}
     \label{BCI CO2 response Parameter Sensitivity}
  \end{figure}

>>>>

\documentclass[draft,linenumbers]{agujournal}
\draftfalse
\usepackage{hyperref}
\usepackage[export]{adjustbox}
\addtolength{\oddsidemargin}{-.875in}
\addtolength{\evensidemargin}{-.875in}

@@

\journalname{Journal of Advances in Modeling Earth Systems (JAMES)}

\begin{document}

 \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/frac_deviation_p1CLM5_CAX__y1.png}
     \caption{Caxiuana State Parameter Sensitivity}
     \label{CAX state}
  \end{figure}

   \begin{figure}[h]
     \centering
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/frac_deviation_p1CLM5_BCI__y1.png}
     \caption{BCI State Parameter Sensitivity}
     \label{BCI state}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/frac_deviation_p1CLM5_ORN__y1.png}
     \caption{Oak Ridge State Parameter Sensitivity}
     \label{ORN state}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/frac_deviation_CO2_response_1CLM5_1x1pt_Br-cax_ens_transient_ELEV_PI_y1.png}
     \caption{Caxiuana CO2 response}
     \label{Caxiuana CO2 response Parameter Sensitivity }
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/frac_deviation_CO2_response_1CLM5_1x1pt_US-ORN_ens_transient_ELEV_PI_y1.png}
     \caption{Oak Ridge CO2 response}
     \label{Oak Ridge CO2 response Parameter Sensitivity}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/frac_deviation_CO2_response_1CLM5_BCI__y1.png}
     \caption{BCI CO2 response}
     \label{BCI CO2 response Parameter Sensitivity}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/rel_GPP.png}
     \caption{GPP CO2 and N respones}
     \label{GPP CO2 and N respones}
  \end{figure}

 \begin{figure}[h]
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/rel_NPP.png}
     \caption{NPP CO2 and N respones}
     \label{NPP CO2 and N respones}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/rel_LAI.png}
     \caption{LAI CO2 and N respones}
     \label{LAI CO2 and N respones}
  \end{figure}
